---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

data(time_series_sample_data)
data(remote_work_by_ed_level)
```

# coriplot

<!-- badges: start -->
[![R-CMD-check](https://github.com/Dashansh/coriplot/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/Dashansh/coriplot/actions/workflows/check-standard.yaml)
<!-- badges: end -->

## Overview

`coriplot` is a dedicated visualization toolkit designed specifically for the [Center On Rural Innovation](https://ruralinnovation.us/). The package extends ggplot2 with customized themes is accordance to the CORI Branding Guidelines as well as a set of utilities tools to make the overall usage more intuitive and seamless.

A comprehensive set of examples is available in the get started section of this website.

## Installation

You can install the development version of coriplot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Dashansh/coriplot")
```

## Example

This is a basic example which shows you how to solve a common problem:
Dashanh's workspace

```{r example1}
library(ggplot2)
library(dplyr)
library(coriplot)

theme_set(theme_cori())
data("remote_work_by_ed_level")
fig <- remote_work_by_ed_level %>%
  ggplot(aes(as.Date(date),
             pct_working_remotely,
             group = education_level,
             color = education_level)) +
  geom_line(lwd = 1.5) +
  xlab("Some Time") +
  ylab("YLabel") +
  labs(title = "This should not exceed\nMore than two lines",
       subtitle = "Some random subtitle",
       caption = "This image is not mine") +
  scale_x_date(date_breaks = "1 month", date_labels =  "%b") + 
  scale_y_continuous(expand = c(0, 0), limits = c(0,NA)) +
  theme_cori()+
  scale_y_percent()

fig

```
